---
title: "TTF Brand Guide"
format: pdf
editor: visual
---

# Tame the Flame Impact Project Brand Guide

## 1. Brand foundation

### Project name

Tame the Flame

### Full project title

Wildfire Risk Reduction Through Hydrated Vegetated Greenbelt Buffers at the Wildland–Urban Interface

### Recommended descriptor

Hydrated landscapes for wildfire resilience

Use the full project title in formal reports, academic materials, and first references. Use Tame the Flame as the short public-facing name in presentations, graphics, outreach materials, and social media

Avoid using “buffer strips” as the primary project name because the project considers a wider range of landscape types, including agricultural lands, riparian corridors, managed open spaces, shaded fuel breaks, and greenbelts

### Positioning statement

Tame the Flame examines how alternative water supplies, landscape management, and policy tools can support vegetated greenbelt buffers as one component of broader wildfire resilience in Santa Barbara County

### Primary audiences

-   Watershed Progressive staff and project partners
-   Santa Barbara County Fire Safe Council and RWMP collaborators
-   Water agencies, wastewater agencies, and stormwater professionals
-   Fire departments, land managers, planners, and regulators
-   Agricultural operators and owners of working lands
-   Community organizations and residents in WUI areas
-   Potential funders and government agencies
-   Academic reviewers and technical experts

### Core values

**Integrated resilience:** Connect water, wildfire, land use, infrastructure, and community planning rather than treating them as separate systems

**Practicality:** Focus on feasible pathways, implementation constraints, and information that can support future decision-making

**Evidence:** Ground recommendations in spatial data, case studies, policy research, modeling, and practitioner experience

**Stewardship:** Recognize the ecological, agricultural, cultural, and community value of managed landscapes

**Collaboration:** Emphasize that implementation will require coordination among agencies, landowners, technical experts, and communities

**Adaptability:** Communicate uncertainty clearly and allow recommendations to change as new data and implementation experience become available

## 2. Logo system

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
